Assessing primitives performance\\ on multi-stage execution

### 2018-05-09 paper.tex
added todo
methodology

\usepackage{xcolor}
\newcommand{\sd}[1]{\color{red}\fbox{\bfseries\sffamily\scriptsize Stef:}{\sf\small$\blacktriangleright$\textit{#1}$\blacktriangleleft$}\color{black}}
\newcommand{\sk}[1]{\color{blue}\fbox{\bfseries\sffamily\scriptsize Sophie:}{\sf\small$\blacktriangleright$\textit{#1}$\blacktriangleleft$}\color{black}}
\newcommand{\cba}[1]{\color{purple}\fbox{\bfseries\sffamily\scriptsize Clement:}{\sf\small$\blacktriangleright$\textit{#1}$\blacktriangleleft$}\color{black}}
\newcommand*\rot{\rotatebox{90}}
\input{macros}

@@

@@

\cba{Methodology section is missing here: each bench was run x times, each time being y comparison. We removed the loop overhead in the measurements. }
\cba{+ we bench only = strings, which could make a difference on the plugin version (one less branch) - maybe we should change to number of character compared instead of string size so it does not imply the string are equals.}
\cba{We are also missing exact results, aside from the graphs I usually expect a table with exact results and error margins... That's why the plot is often generated from a file, the table can reuse the same file and you can re-do your bench without changing the latex code. Cf https://hal.inria.fr/hal-01596321/document page 9, it would be nice here to have a similar table below the benchs}

@@

\cba{Maybe talk in those cases the number of representation of the primitives}

@@

\section{Future work and conclusion}
1. number of representations\\
2. common representation
\cba{Future work -> primitive processor dependent (i.e. SSE4 instrs), pros and cons and why you did not do it (ingeniering cost per back-end)}
\cba{Inlining in Sista + ref}
\cite{SistaFastStartUp}

@@

%% Appendix
\appendix
\section{Smart Syntax code}
\label{SmartSyntaxAppendix}

>>>>

\usepackage{xcolor}
\newcommand{\todo}[1]{\color{orange}\fbox{\bfseries\sffamily\scriptsize TODO:}{\sf\small$\blacktriangleright$\textit{#1}$\blacktriangleleft$}\color{black}}
\newcommand{\sd}[1]{\color{red}\fbox{\bfseries\sffamily\scriptsize Stef:}{\sf\small$\blacktriangleright$\textit{#1}$\blacktriangleleft$}\color{black}}
\newcommand{\sk}[1]{\color{blue}\fbox{\bfseries\sffamily\scriptsize Sophie:}{\sf\small$\blacktriangleright$\textit{#1}$\blacktriangleleft$}\color{black}}
\newcommand{\cba}[1]{\color{purple}\fbox{\bfseries\sffamily\scriptsize Clement:}{\sf\small$\blacktriangleright$\textit{#1}$\blacktriangleleft$}\color{black}}
\newcommand*\rot{\rotatebox{90}}
\input{macros}

@@

 \todo{Finish section}

@@

\subsection{Methodology}

\todo{fill methodology section}
\cba{missing here: what are the benchmark actually run ? Can be short code sample or explanation of both. It has to include: each bench was run x times, each time being y comparison. We removed the loop overhead in the measurements.}
\cba{+ we bench only = strings, which could make a difference on the plugin version (one less branch) - maybe we should change to number of character compared instead of string size so it does not imply the string are equals.}
\cba{SM methodology: what is done? which benchmarks are used? how are they executed? what is measured? how do you address warmup etc? what kind of machine is used for the measurements?}

\todo{Add exact results}
\cba{We are also missing exact results, aside from the graphs I usually expect a table with exact results and error margins... That's why the plot is often generated from a file, the table can reuse the same file and you can re-do your bench without changing the latex code. Cf https://hal.inria.fr/hal-01596321/document page 9, it would be nice here to have a similar table below the benchs}

@@

\cba{Maybe talk in those cases the number of representation of the primitives, this is a bit disconnected with the rest of the paper I feel}

@@

\section{Future work and conclusion}
\todo{Write section}

\paragraph{Future work.}
\cba{Future work -> primitive processor dependent (i.e. SSE4 instrs), pros and cons and why you did not do it (ingeniering cost per back-end)}
\cba{Inlining in Sista + ref}
\cite{SistaFastStartUp}

1. number of representations\\
2. common representation

@@

\todo{Add some intro sentence here and there + maybe ASM in appendix}
%% Appendix
\appendix
\section{Smart Syntax code}
\label{SmartSyntaxAppendix}
